This is the title [Article v\versionnumber]

### 2022-09-15 manuscript/manuscript.tex
Make Intro more solvation-focused, add some references.

The computational calculation of thermodynamical solvation properties is therefore of particular interest and has been tackled by a wide array of methods.
Quantum mechanical methods provide the most rigorous description of the underlying potential energy surface (PES) but suffer from high computational cost, allowing only the treatment of small systems and few solvent molecules. 
%More recently, QM/MM approaches and potentials based on deep learning \cite{Smith2017-ani} are trying to bridge the gap to computationally less demanding methods while keeping the accuracy of DFT methods.

\todo{Remove the part about QM vs.\ MM. We are doing MD and cite ALL solvation methods. COSMO, other implicit solvents, information theory, QSAR, Pratt and coworkers, Mobley and coworkers}
Molecular mechanics based approaches describe the underlying PES through empirically fit force-fields, which reduce the computational demand of these calculations tremendously.
This allows for the treatment of large biological systems such as proteins in aqueous solution.
Implicit solvent methods such as MM/PBSA or MM/GBSA \cite{Sitkoff1994-pbsa,Kollman2000-mmpbsa} can quickly provide results for a large number of structures, but yield inaccurate results when compared to more rigorous explicit solvent methods \cite{Genheden2015-mmpbsa-review}.
On the other hand, the free energy of solvation can be calculated in a statistically rigorous way using explicit solvent simulations combined with alchemical methods such as free energy perturbation (FEP) \cite{Zwanzig1954-reweighting} or thermodynamic integration(TI) \cite{Kirkwood1935-ti}.
However, they are unable to provide a spatial interpretation of the results.
Furthermore, splitting the resulting free energy into contributions for the enthalpy and entropy is challenging \cite{Peter2004-alchemical-entropy}.
%Assuming sufficient sampling, they can accurately predict the free energy of solvation in the boundaries of the assumptions underlying their forcefield. 
%However, the seperation of enthalpic and entropic contributions to the free energy of solvation is difficult with these methods and localizing these contributions not easily possible.

>>>>

%The computational calculation of thermodynamical solvation properties is therefore of particular interest and has been tackled by a wide array of methods.
%Quantum mechanical methods provide the most rigorous description of the underlying potential energy surface (PES) but suffer from high computational cost, allowing only the treatment of small systems and few solvent molecules. 
%More recently, QM/MM approaches and potentials based on deep learning \cite{Smith2017-ani} are trying to bridge the gap to computationally less demanding methods while keeping the accuracy of DFT methods.

A wide range of methods have been devised to compute the free energy of hydration.
Data-driven methods such as QSPR or UNIFAC can deliver good results \cite{Borhani2019-qspr,Fredenslund1975-unifac}, but might be limited to molecules that are similar to those in the training set.
Polarizable continuum models (PCMs) \cite{Miertus1981-pcm,Klamt1993-cosmo} such as treat the solvent phase as a homogeneous phase that reacts to the electrostatic potential of the solute \cite{Mennucci2010-pcm}.
%Molecular mechanics based approaches describe the underlying PES through empirically fit force-fields, which reduce the computational demand of these calculations tremendously.
%This allows for the treatment of large biological systems such as proteins in aqueous solution.
Methods such as MM/PBSA or MM/GBSA \cite{Sitkoff1994-pbsa,Kollman2000-mmpbsa} combine an implicit solvent treatment of electrostatics with structural sampling of the solute.
They can quickly provide results for a large number of structures, but yield inaccurate results when compared to more rigorous explicit solvent methods \cite{Genheden2015-mmpbsa-review}.

On the other hand, explicit solvation methods model the solvent using individual molecules.
They are generally more accurate than implicit methods, but require a statistical sampling of the solvent conformations \cite{Liu2016-md-solubility,Swails2014-cphmd}.
Molecular dynamics (MD) simulations provide an accurate way of modeling solvent packing in confined areas \cite{}\todo{ask Tom for a citation!} and general hydrophobic effects \cite{Pratt2016-hydrophobicity}.

The free energy of solvation can be calculated in a statistically rigorous way using alchemical methods \cite{Liu2016-md-solubility,Mobley2009-dgsolv,Mobley2014-freesolv} such as free energy perturbation (FEP) \cite{Zwanzig1954-reweighting} or thermodynamic integration (TI) \cite{Kirkwood1935-ti}.
However, they are unable to provide a spatial interpretation of the results.
Furthermore, splitting the resulting free energy into contributions for the enthalpy and entropy is challenging \cite{Peter2004-alchemical-entropy}.
%Assuming sufficient sampling, they can accurately predict the free energy of solvation in the boundaries of the assumptions underlying their forcefield. 
%However, the seperation of enthalpic and entropic contributions to the free energy of solvation is difficult with these methods and localizing these contributions not easily possible.
